NumPy---Array Programming in Python

### 2020-02-15 body.tex
Minor change to Fig. 1
Add references to discussion

The developer culture has matured: while initial development was
highly informal, NumPy now has a roadmap and a process for proposing
and discussing large changes.  The project has formal governance
structures and is fiscally sponsored by NumFOCUS, a nonprofit that
promotes open practices in research, data, and scientific computing.
Over the past few years, the project attracted its first funded
development, sponsored by the Moore and Sloan Foundations, and
received an award as part of the Chan Zuckerberg Initiative's
Essentials of Open Source Software program.  With this funding, the
project was (and is) able to have sustained focus over multiple months
to implement substantial new features and improvements.  That said, it
still depends heavily on contributions made by graduate students and
researchers.

@@

Over the next decade, we will face several new challenges.
%Artificial
%Intelligence and Data Science will mature ... [what do we say about
%  this?].
New devices will be developed, and existing specialized
hardware will evolve, to meet diminishing returns on Moore's law.
There will be more, and a wider variety of, data science
practitioners, a significant proportion of whom will be using NumPy.
The scale of scientific data gathering will continue to expand, with
the adoption of devices and instruments such as light sheet
microscopes and the LSST.  New generation languages, interpreters, and compilers,
such as Rust, Julia, and LLVM, will invent and determine the viability
of new concepts and data structures.

>>>>

The developer culture has matured: while initial development was
highly informal, NumPy now has a roadmap and a process for proposing
and discussing large changes.  The project has formal governance
structures and is fiscally sponsored by NumFOCUS, a nonprofit that
promotes open practices in research, data, and scientific computing.
Over the past few years, the project attracted its first funded
development, sponsored by the Moore and Sloan Foundations, and
received an award as part of the Chan Zuckerberg Initiative's
Essentials of Open Source Software program.  With this funding, the
project was (and is) able to have sustained focus over multiple months
to implement substantial new features and improvements.  That said, it
still depends heavily on contributions made by graduate students and
researchers in their free time.

@@

Over the next decade, we will face several new challenges.
%Artificial
%Intelligence and Data Science will mature ... [what do we say about
%  this?].
New devices will be developed, and existing specialized
hardware will evolve, to meet diminishing returns on Moore's law.
There will be more, and a wider variety of, data science
practitioners, a significant proportion of whom will be using NumPy.
The scale of scientific data gathering will continue to expand, with
the adoption of devices and instruments such as light sheet
microscopes and the LSST \cite{jenness2018lsst}.  New generation languages, interpreters, and compilers,
such as Rust \cite{10.1145/2692956.2663188}, Julia \cite{Julia-2017}, and LLVM \cite{LLVM:CGO04}, will invent
and determine the viability of new concepts and data structures.
